Maenpuen et al. Appendix S1-7: Sources and consequences of mismatch between leaf disc and whole-leaf leaf mass per area (LMA)

### 2022-05-03 ms/LMA_method.Rmd
update ms

Leaf tissue density, leaf area and leaf thickness influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 1).
Specifically, species with greater leaf tissue density (Fig. 1a, $\beta_1$), and larger (Fig. 1a, $\beta_2$) and thicker leaves (Fig. 1a, $\beta_3$) had greater whole-leaf LMA than leaf disc LMA.
Species with lower leaf tissue density (Fig. 1b, $\gamma_1$), larger leaf area (Fig. 1b, $\gamma_2$), and thinner leaves (Fig. 1b, $\gamma_3$) had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.

When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.
Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1% greater than disc-based estimates in the arithmetic scale (Table 1).
Intercepts did not differ for small-leaved species (Table 1).

@@

![](../figs/coef_sp3.png)

>>>>

Leaf tissue density, leaf area and leaf thickness influenced the relationship between the whole-leaf LMA and leaf disc LMA (Fig. 1).
Specifically, species with lower leaf tissue density (Fig. 1a, $\beta_1$) and larger leaves (Fig. 1a, $\beta_2$) had greater whole-leaf LMA than leaf disc LMA.
Species with lower leaf tissue density (Fig. 1b, $\gamma_1$) and larger larger leaves (Fig. 1b, $\gamma_2$) also had larger variance in the relationship between the whole-leaf LMA and leaf disc LMA.
Thinner-leaved species (Fig. 1b, $\gamma_3$) tended to have larger variance in the relationship (i.e., the 90% credible interval did not include zero).

When we pooled all the species, there were significant differences in intercepts for species mean LMA (Table 1), suggesting that the whole-leaf estimates of LMA were 9.4% greater than disc-based estimates in the arithmetic scale.

Large-leaved species also had significant positive intercepts, suggesting that whole-leaf estimates of LMA were 22.1% greater than disc-based estimates in the arithmetic scale (Table 1).
Intercepts did not differ for small-leaved species (Table 1).

@@

![](../figs/coef_sp31.png)
